Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-19 GWLDCII.tex
fix the item 5 problem

  \begin{proof}
[See Figure \ref{fig new le diagrams}]

By Lemma~\ref{lem I} we have $I_1^W = I_1^V\cup \{n-3\}$ and $I_{n-2}^W = (I_n^V \setminus \{n-5\}) \cup \{n-1,n-2\}$. By equation \eqref{eq necklace} we have $n-5 \in I_1^V$, and by the following discussion we have $n-1,n-2,n-3 \not\in I_n^V,I_1^V$. It follows that the symmetric difference of $I_1^W$ and $I_{n-2}^W$ is:
    \begin{gather*}
    I_1^W \setminus I_{n-2}^W = (I_1^V\cup\{n-3\}) \setminus \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) = (I_1^V\setminus I_n^V) \cup \{n-3, n-5\}. \\
    I_{n-2}^W \setminus I_1^W = \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) \setminus(I_1^V\cup\{n-3\}) = (I_n^V\setminus I_1^V) \cup \{n-1, n-2\}.
\end{gather*}
As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{a\}$, where $a$ is the second ``something'' in equation \eqref{eq necklace}. If $a \neq n-4$ then the path from $I_n^V$ lies above the paths from $\{n-3, n-5\}$ and $\{n-2, n-1\}$ and we obtain point 1.

@@

  \begin{lem}\label{lem n-2 bad part 2}
    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then:
    \begin{enumerate}
  \item $c=n-4$ if $n-4\in I_1^V\setminus I_n^V$ and $c=n-5$ otherwise.
  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $c\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.  $I_{n-2}^W$ does not contribute this $+$ but yields the $c\rightarrow (n-1)$ plus from Lemma~\ref{lem n-2 bad part 1}
  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
  \item No element of the Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus.  Additionally if $c=n-4$ then no element of the Grassmann necklace of $V$ contributes an $(n-5)\rightarrow n$ plus and only $I_n^V$ contributes an $(n-4)\rightarrow n$ plus.
  \end{enumerate} 
\end{lem}

@@

  Now in the case that $I_{n-2}^V$ contribued an $(n-4)\rightarrow (n-2)$ plus, then going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so instead of the $(n-4)\rightarrow (n-2)$ plus and the $(n-5)\rightarrow (n-1)$ plus we have an $(n-4)\rightarrow (n-1)$ plus, but the rest stays the same.  Also, in going from $I_{n-3}^V$ to $I_{n-2}^V$, $n-3$ comes out and $n-2$ goes in so all that changes is a $(n-4)\rightarrow (n-3)$ path becomes an $(n-4)\rightarrow (n-2)$ path.
\item The only elements which could contribute an $(n-5)$ path are those without an $n-5$.  From \eqref{eq necklace} the only ones without an $n-5$ are $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$, but the calculations above show they do not have paths as described above.  Also, if $c=n-4$ then $n-4\in I_1$ so the only elements which could contribute an $(n-4)$ path are those which contain an $n-4$ which are $I_{n}$, $I_{n-1}$, $I_{n-2}$, $I_{n-3}$, which we explicitly see do not.
  \end{enumerate}
\end{proof}

@@

  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lLmma and subsequent discussion.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.  Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.  This bijection can be described as follows:
  \begin{itemize}
  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
  \end{itemize}
  Note that this map is reversible and hence bijective. Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points. However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e. the first bullet point does not apply.

>>>>

  \begin{proof}

Figure \ref{fig new le diagrams} illustrates the cases appearing in this proof.

By Lemma~\ref{lem I} we have $I_1^W = I_1^V\cup \{n-3\}$ and $I_{n-2}^W = (I_n^V \setminus \{n-5\}) \cup \{n-1,n-2\}$. By equation \eqref{eq necklace} we have $n-5 \in I_1^V$, and by the following discussion we have $n-1,n-2,n-3 \not\in I_n^V,I_1^V$. It follows that the symmetric difference of $I_1^W$ and $I_{n-2}^W$ is:
    \begin{gather*}
    I_1^W \setminus I_{n-2}^W = (I_1^V\cup\{n-3\}) \setminus \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) = (I_1^V\setminus I_n^V) \cup \{n-3, n-5\}. \\
    I_{n-2}^W \setminus I_1^W = \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) \setminus(I_1^V\cup\{n-3\}) = (I_n^V\setminus I_1^V) \cup \{n-1, n-2\}.
\end{gather*}
As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{v\}$. If $v \neq n-4$ then the path from $I_n^V$ lies above the paths from $\{n-3, n-5\}$ and $\{n-2, n-1\}$ and we obtain point 1.

@@

  \begin{lem}\label{lem n-2 bad part 2}
    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then:
    \begin{enumerate}
  \item $c=n-4$ if $n-4\in I_1^V\setminus I_n^V$ and $c=n-5$ otherwise.
  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $c\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.  $I_{n-2}^W$ does not contribute this $+$ but yields the $c\rightarrow (n-1)$ plus from Lemma~\ref{lem n-2 bad part 1}
  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
  \item The Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus if and only if $n-4\in I_1^V\setminus I_n^V$.
  \end{enumerate} 
\end{lem}

@@

  Now in the case that $I_{n-2}^V$ contribued an $(n-4)\rightarrow (n-2)$ plus, then going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so instead of the $(n-4)\rightarrow (n-2)$ plus and the $(n-5)\rightarrow (n-1)$ plus we have an $(n-4)\rightarrow (n-1)$ plus, but the rest stays the same.  Also, in going from $I_{n-3}^V$ to $I_{n-2}^V$, $n-3$ comes out and $n-2$ goes in so all that changes is a $(n-4)\rightarrow (n-3)$ path becomes an $(n-4)\rightarrow (n-2)$ path.
\item The only elements which could contribute an $(n-5)$ path are those without an $n-5$.  From \eqref{eq necklace} the only ones without an $n-5$ are $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$.  \note{find the right pluss or lack thereof}.
  \end{enumerate}
\end{proof}

@@

  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lLmma and subsequent discussion.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.  Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.  This bijection can be described as follows:\note{In the case $n-4\in I_1^V \setminus I_n^V$ then the $ (n-4)\rightarrow (n-1)$ plus is not new in $W$ but instead there is an $(n-5)\rightarrow (n)$ plus in $W$ which gives the third new plus.  This needs to be added to the proof and the rest adjusted for the bad $n-4$ possiblity.}
  \begin{itemize}
  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
  \end{itemize}
  Note that this map is reversible and hence bijective. Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points. However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e. the first bullet point does not apply.
